---
title: "lab2"
author: "Esme, Zach, Mandi"
date: "1/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-data}
install.packages("fivethirtyeight")
remotes::install_github("fivethirtyeightdata/fivethirtyeightdata")
install.packages("formattable")
library(fivethirtyeight)
library(fivethirtyeightdata)
library(tidyverse)
library(formattable)
library(ggridges)
library(lubridate)
library(tm)
```

```{r}
google <- google_trends
tv <- tv_states
q3 <- comic_characters
```

Need to pivot_longer() to make single vector with "hurricane)
```{r}
goog_longer <- pivot_longer(data = google,
             cols = 2:5,
             names_to = "hurricane",
             values_to = "trends")
```

```{r}
ggplot(goog_longer, aes(date, trends)) +
  geom_line(aes(color = hurricane)) +
  geom_point(aes(color = hurricane,
                 shape = hurricane))
```





<!-- Zach, check code chunk below and right after to see which is correct -->
Visualize with solid shapes NEED TO DOOOOO
```{r}
ggplot(goog_longer) +
  geom_point(aes(date, trends, 
                 color = hurricane,
                 shape = hurricane)) #Is this what he means by visualizing with solid shapes?

?geom_ribbon
ggplot(goog_longer, aes(date)) +
  geom_ribbon(aes(ymin = 0, ymax=trends, fill = hurricane)) #or is this what he wants?
```

Visualize with solid shapes
```{r}
?geom_ribbon
ggplot(goog_longer, aes(date, trends)) +
  geom_point(aes(shape = hurricane,
                 color = hurricane))
```





<!-- Zach, same here with the two code chunks below -->
Visualize the same relation, but change the scales so color is mapped to a continuous scale (the other scales should be discrete).
```{r}
ggplot(goog_longer) +
  geom_point(aes(hurricane, date,
                 color = trends), size = 3) # is this what he is looking for?
```

Visualize the same relation, but change the scales so color is mapped to a continuous scale (the other scales should be discrete).
```{r}
id <- 1:4
hurricane_name <- c("Harvey", "Irma","Jose", "Maria")
landfall <- c("2017-08-2017", "2017-10-2017", "NA", "2017-09-2017")
df <- data.frame(id, hurricane_name, landfall)
```

<!-- And Zach, this is the same code chunk as above but a different title? -->
Make DataFrame
```{r}
id <- 1:4
hurricane_name <- c("Harvey", "Irma","Jose", "Maria")
landfall <- as.Date(c("2017-08-25", "2017-09-10", "NA", "2017-09-20"))
df <- data.frame(id, hurricane_name, landfall)
```

Add Vline
```{r}
ggplot(goog_longer, aes(date, trends)) +
  geom_line(aes(color = hurricane)) +
  geom_vline(xintercept = df$landfall) #Still need to figure out how to either make them match the colors of goog_longer$hurricane or to add labels to the vlines
```

Q2...Mandi's part
Needed to pivot_longer and convert data to percentage
```{r}
tv_longer <- pivot_longer(data = tv,
             cols = 2:4,
             names_to = "state",
             values_to = "share")
#used pivot_longer to combine states into one column and put their values in another

df2 = data.frame(tv_longer$date, tv_longer$state, tv_longer$share)
df2$tv_longer.share <- percent(df2$tv_longer.share)
df2

#converted values to percentages

```

Replication of visualization 
```{r}
df2 %>% 
  ggplot(aes(tv_longer.date, tv_longer.share)) +
  geom_line(aes(color = tv_longer.state)) +
  labs(x = "", 
       y = "Share of sentences", 
       title = "National cable news networks", 
       caption = "Includes Bloomberg, CNBC, CNN, Fox Business, Fox News and MSNBC.")
 
df2 %>% 
ggplot(aes(tv_longer.date, tv_longer.share)) +
  geom_ribbon(aes(ymin = -Inf, xmin = -Inf, xmax = Inf, ymax = tv_longer.share, fill = tv_longer.state)) +
  labs(x = "", 
       y = "Share of sentences", 
       title = "National cable news networks", 
       caption = "Includes Bloomberg, CNBC, CNN, Fox Business, Fox News and MSNBC.") +
  theme_minimal() +
  theme(legend.title=element_blank()) +
  scale_fill_manual(values=c("hot pink", "#00a4b3", "dark orange"), name="fill")

?geom_ribbon
  
 #mutate(tv_longer.date = fct_relevel(tv_longer.date, "AUG. 15. 2017", "SEPT. 1", "SEPT. 15", "OCT. 1")) %>% 
```

Q3. comic_characters dataset
<!-- working on making prettier and reordering; want another kind besides bar charts -->
```{r}
# get proportions
df <- q3 %>%
  mutate(sex = tolower(sex)) %>% 
  count(sex)

# removing word characters from column 'sex'
## using tm library here

stopwords = readLines('stopwords.txt')
x  = df$sex
x  =  removeWords(x,stopwords)
df$sex_new <- x

# proportion by publisher
df_p <- q3 %>%
  group_by(publisher) %>% 
  mutate(sex = tolower(sex)) %>% 
  count(sex)

# removing word characters from column 'sex'
## using tm library here

stopwords = readLines('stopwords.txt')
x  = df_p$sex
x  =  removeWords(x,stopwords)
df_p$sex_new <- x

# Provide 3 different visuals
df %>% 
  mutate(number = n + 0) %>% 
  select(-c(sex, n)) %>% 
  ggplot(aes(fct_infreq(sex_new), number)) +
  geom_point() +
  theme_minimal() +
  labs(x = "Gender",
       y = "Comic Characters",
       title = "Gender of Comic Characters")

q3 %>% 
  count(sex, sort = TRUE) %>% 
  mutate(sex = reorder(sex, n)) %>%
    ggplot(aes(n, sex)) +
    geom_col(fill = "#ffa200") +
  theme_minimal() +
  labs(x = "Gender",
       y = "Comic Characters",
       title = "Gender of Comic Characters")

df_p %>% 
  mutate(number = n + 0) %>% 
  group_by(publisher) %>% 
  ggplot(aes(sex_new,number)) +
  geom_col(fill = "seagreen4") +
  geom_text(aes(label = number), vjust = -0.5) +
  facet_wrap(~publisher) +
  theme_minimal() +
  labs(x = "Gender",
       y = "Comic Characters",
       title = "Gender and the Universes")
```
